A Decision Procedure for (Co)datatypes in SMT Solvers\thanks{In memoriam Morgan Deters 1979--2015}

### 2016-04-15 sister/sister.tex
Add reference to application paper.

In the past decade, satisfiability modulo theories (SMT) solvers
\cite{nieuwenhuis-et-al-2006}
% \cite{ganzinger-et-al-2004}
have emerged as one of the most powerful ways to prove theorems in classical
first-order logic. These solvers are also useful for constraint solving, or model finding:
Given some constraints, they can be used to find an assignment, or model, that
satisfies them.

>>>>

In the past decade, satisfiability modulo theories (SMT) solvers
\cite{nieuwenhuis-et-al-2006}
% \cite{ganzinger-et-al-2004}
have emerged as useful tools in a number of applications~\cite{DeMoura2011SMT}.
These solvers are one of the most powerful ways to prove theorems in classical
first-order logic, and are also useful for constraint solving, or model finding:
Given some constraints, they can be used to find an assignment, or model, that
satisfies them.
